A thesis draft

### 2018-11-19 res/sections/09-RelatedWork.tex
Add preliminar part about related works

A virtualized EPC implementation has been describe in~\cite{hawilo2014nfv}
% TODO talk about vEPC

It is interesting to note that, between all the possibile and alternative
related works we have been albe to find, none of these used Docker as an
alternative virtualization approach.

>>>>

A virtualized EPC implementation, designed to allow mobile broadband services in
the UMTS/LTE world, has been described in~\cite{hawilo2014nfv}, showing how this
implementation is able, thanks to entities grouping, to perform better than a
traditional EPC installation. In~\cite{afolabi2017end} is possible to read
another vEPC implementation, where the Wireless Netowrk Virtualization (WNV),
SDN and NFV (identified from the authors as key elements in order to implement
the 5G architecture) are virtualized, and ported as a service (defined as
EPCaaS) across multi-domains clouds. The realization of such framework is
pursued thanks to end-to-end network slicing.
% talk about end-to-end network slicing

It is interesting to note that, between all the possibile and alternative
related works we have been albe to find, none of these used an only
container-based approach.
